\hyphenation{diffe-rent}
%%%%%%%%%%%%%%%%%%%%% Conclusions %%%%%%%%%%%%%%%%%
\chapter{Conclusions}
\label{ch:Conclusions}

In this dissertation, a search for double Higgs boson production (HH) mediated by a KK graviton or a radion is presented. The double Higgs system subsequently decays through the intermediate $bbZZ$ state - one of the Higgs bosons decays to two b quarks, while the other decays to a pair of Z bosons, which, in turn, decay to a pair of neutrinos and a pair of electrons or muons. The search is performed in data samples corresponding to an integrated luminosity of 35.9 fb$^{-1}$ at $\sqrt s =13$ TeV, recorded by the CMS experiment at the LHC in 2016. 

This is the first in the world ever search for double Higgs boson production in the $bbZZ$ intermediate channel. A measurement of double Higgs production process is an important test of the standard model (SM) and can open doors to beyond the standard model physics. The HH process, observed in a resonant production mode, would mean new physics, while the HH process observed in a non-resonant mode at the SM predicted level allows one to study Higgs boson self-coupling. 

No statistically significant deviations from the SM predictions for background processes were observed in this measurement, and 95\% upper-level confidence limits are reported for the production cross section of a KK graviton or a radion multiplied by the branching fraction of its subsequent decay into a di-Higgs system, and further to the $2 b 2 \ell 2 \nu$ final state. The limits are derived for resonance masses in the 250 GeV to 1 TeV range.

This measurement was released to the public in November 2018. The measurement is part of an intensive program of searching for a di-Higgs production in CMS in a wide range of channels. Current projections suggest that if no new physics is found, the first observation of this process is not expected in any individual HH channel in the near future. The CMS plan is to combine several HH channels. Present CMS searches in $bbZZ$ channels with different final states will be combined, and then added to a combination of the CMS HH searches in other channels.
