This the first ever bbZZ analysis performed at CERN with the real data uses the standard set of the CMS
reconstructed physics objects. We describe reconstruction of
electrons, muons, jets and b jets, and MET separately below:



\subsection{Electrons\label{sec:electrons}}
The Gaussian Sum Filter algorithm (GSF
Electrons)~\cite{Khachatryan:2015hwa} is used to reconstruct
electrons. GSF helps to estimate track parameters. The procedure starts as follows: a mixture of Gaussian distributions (normally about 4-6 components) \ref{GSF} is used to estimate the energy loss in each layer of the tracker. The energy loss is modelled by the Bethe-Heitler formula. Two most important track properties are then computed: a weighted mean or the most frequent value (mode). The first estimate is unbiased while the latter one has a smaller width. In practice, mostly one works with the mode. Gaussian mixtures are determined minimising either the absolute difference between the CDFs of the model and of the Gaussian mixture, or the Kullback-Leibner distance, which is a logarithm of the ratio of the pdfs of the model with respect to the mixture. Finally, the tracks are extrapolated further to the ECAL The measurement selects electrons, which pass the following selection:
%loose set of preselection cuts in applied,
%namely, 
leading electron $\pt>25\GeV$ and subleading electron $\pt>15\GeV$, $|\eta|<2.5$, 
%$d_{xy}<0.05\cm$, $d_z<0.2\cm$ and 
an isolation cut of 0.06, for which the cone
of $0.3$ is used to compute the $\rho$-subtracted PF
isolation. Lepton isolation is calculated as a scalar sum of
the transverse momentum $(p_{T})$ of all the charged and
neutral hadrons as well as photons around the lepton
(excluding the cone) normalised to the $p_{T}$ of the lepton
itself. 
%POG recommended MVA ID WP Loose is further applied to the set of selected electrons.
%The cut on isolation in the measurement for electrons is $0.06$.

        
        %%To emulate the conditions of the HLT trigger, a set of offline cuts is applied further.

%% \texttt{pt>15 \& (}\\
%% \texttt{(abs(superCluster().eta)<1.4442 \& full5x5\_sigmaIetaIeta<0.012 \& }\\
%% \texttt{hcalOverEcal<0.09 \&}\\
%% \texttt{(ecalPFClusterIso/pt)<0.4 \& (hcalPFClusterIso/pt)<0.25 \&}\\
%% \texttt{(dr03TkSumPt/pt)<0.18 \& abs(deltaEtaSuperClusterTrackAtVtx)<0.0095 \&}\\
%% \texttt{abs(deltaPhiSuperClusterTrackAtVtx)<0.065) || }\\
%% \texttt{(abs(superCluster().eta)>1.5660 \& full5x5\_sigmaIetaIeta<0.033 \&}\\
%% \texttt{hcalOverEcal<0.09 \&}\\
%% \texttt{(ecalPFClusterIso/pt)<0.45 \& (hcalPFClusterIso/pt)<0.28 \&}\\
%% \texttt{(dr03TkSumPt/pt)<0.18)}\\
%% \texttt{).}

        On top of the selection defined above, a specific CMS Particle Object Group (POG) recommended working point (WP) is applied, which is a discriminant based on the a multivariate analysis (MVA) for classification of signal/background electrons. The WP consists of nearly 20 variables utilising the information from the impact point, tracks, and the ECAL: $\chi^2 variables$ of the track and the quality of its estimate, $\delta \eta$, $\delta \phi$, energy of the 3 by 3 cluster, ECAL energy over momentum, etc. For this analysis we use the loose working point (another name can be WP90), as described in ~\cite{vhbbAN}. ID and ISO, as well as the HLT SFs are applied.
%        \small{\texttt{https://twiki.cern.ch/twiki/bin/viewauth/CMS/ \\MultivariateElectronIdentificationRun2}}
%\normalsize



\subsection{Muons\label{sec:muons}}
        In this analysis we are using global muons reconstructed using the information from the tracker and muon system \cite{CMS-PAS-MUO-10-002,Chatrchyan:2012xi}. During the offline reconstruction, muons chambers segments are used as seeds for the "standalone muon" reconstruction. The seed is a position, a direction, and an initial momentum of the muon candidate. This serves as an input to the track fitting procedure utilising muon system information. The resulting object after executing this technique is what is called a standalone muon. Then, for each standalone muon the algorithm searches for the tracks reconstructed in the inner tracking system (tracker tracks) that would match the muon. Then for each standalone muon - tracker track pair the Kalman filter based fit is performed. The result is a collection of muons which are referred to as global muons. In this analysis the kinematic and isolation selection of global muons is the following:
        
        
        
        
        
        
        
        
        
        
        
        
        
        
        
leading muon $\pt>20\GeV$ and subleading muon $\pt>15\GeV$, $|\eta|<2.4$,
%re is a loose preselection of $\pt>5\GeV$, $|\eta|<2.4$, $d_{xy}<0.5\cm$, $d_z<1.0\cm$, as well as 
a relative
isolation cut of 0.15, with the cone of $0.4$ used to compute $\Delta\beta$-subtracted PF isolation.
Finally, a tighter selection - muon POG recommended WP Loose is applied.~\cite{MuonsRun2}. ID, ISO, HLT and tracker SFs are applied.
%The offline cut on isolation for muons is $0.15$.
%% Loose muon:
%% \begin{itemize}
%%   \item  Particle-Flow Muon:\\
%% \texttt{isPFMuon()}
%%   \item  is Global or Tracker Muon:\\
%% \texttt{isGlobalMuon() || isTrackerMuon()}
%%  \end{itemize}

\subsection{Jets\label{sec:jets}}
    Particle flow algorithm is used to reconstruct jets\cite{CMS-PAS-PFT-09-001,CMS-PAS-PFT-10-001}, with the help of the  $\text{anti}-k_T$ clustering algorithm having a distance parameter of $R=0.4$~\cite{Cacciari:2005hq,Cacciari:2008gp}.
    Reconstructed jets are further corrected for detector effects using specific corrections determined from the data and MC. Only jets passing $|\eta|<2.4$ and  $(\pt > 30\GeV)$ are considered for the analysis. 
    All the necessary jet energy resolution (JER) and jet energy scale (JES) corrections provided by the JetMET group are applied ~\cite{JetMETgroup}.

%following this twiki:
%\begin{center}
 %   \texttt{https://twiki.cern.ch/twiki/bin/viewauth/CMS/JetResolution}    
%\end{center}

\subsection{Identification of b jets\label{sec:bjets}}
MVA technique combining the information about the impact parameter, identified secondary vertices, as well as soft lepton (if any) contained inside of the jet is used by the CMVA algorithm to identify b quark originated jets. The output is a continuous MVA discriminant ranging in value from -1 to +1. Optimal cut is determined by the POG for several working points. We use CMVAv2 medium working point  $(>0.4432)$. We checked all three WPs and WP Medium gives the best limits. b tag and mistag corrections are applied.

%\clearpage


\subsection{Missing transverse energy}\label{sec:MET}

MET type-1 corrected is calculated as an absolute value of the negative vector sum of all the visible PF candidates in the event. Then all the necessary corrections recommended by the POG are applied ~\cite{MissingETRun2Corrections} and on top, a set of filters related to the instrumental effects is employed ~\cite{MissingETOptionalFiltersRun2}. 
%following the twiki:
%\begin{center}
%\texttt{https://twiki.cern.ch/twiki/bin/viewauth/CMS/MissingETRun2Corrections}
%\end{center}
%On top, a set of filters related to the instrumental effects is employed:
%\begin{center}
%\texttt{https://twiki.cern.ch/twiki/bin/view/CMS/MissingETOptionalFiltersRun2}
%\end{center}
